---
documentclass: article
fontsize: 10pt # Options Include 10pt, 11pt, or 12pt
header-includes:
- \usepackage{crimson}
- \usepackage[T1]{fontenc}
- \usepackage[margin=1in]{geometry}
- \renewcommand{\baselinestretch}{1}
- \usepackage{calc}
- \usepackage{enumitem}
- \usepackage{changepage}
output:
  pdf_document:
    number_sections: yes # Yes if you wanted numbered sections
  word_document: default
urlcolor: blue
---

<!---Note. This memo template is not intended to work with a Table of Contents. Do Not try to include a table of contents in this template.--->
<!---THE MEMO HEADER. Edit Only The Text Next to \item--->

\vspace{-85pt}
\text{\bfseries\LARGE{ENGAGE 2.0: Uganda SEL Data Health Report}}
\newline
\vspace{-10pt}
\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}
\vspace{-9pt}
\setlist[2]{noitemsep}
\begin{description}[leftmargin=!,itemsep=-1ex,labelwidth=\widthof{Subject:  }]
  \item[Subtitle:] \bfseries{Daily Endline Assessment Brief}
  \item[By:]Advisory, Street Child 
  \item[Date:] `r format(Sys.time(), '%B %d, %Y')`
\end{description}
\vspace{-10pt}
\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}
\vspace{-25pt}

<!---THE MEMO BODY. EDITS ALL PLAIN TEXT--->

## Context
\vspace{-10pt} <!---Adjust space between headers and paragraph text as needed--->

```{r Script, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# source("Scripts/Quality.R", local = knitr::knit_global())
library(kableExtra)
```



## Header I

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
kbl(Duration, caption = "Survey duration (mins) across enumerators", booktabs = T) %>%
kable_styling(latex_options=c("striped","hold_position")#,stripe_index = c(3, 11, 13)
              ) %>%
  # row_spec (c(3, 11, 13), italic=T, color = "#fba536") %>%
  column_spec(1, width ="9cm")
```

## Header II
```{r echo=FALSE, fig.height=4, fig.width=9, message=FALSE, warning=FALSE, paged.print=FALSE}
dr
```








<!---BELOW ARE YOUR MEMO CITATIONS. ---> 
<!---Note: Ensure the number of citations below matches the citation marks included above. --->

<!-- [^1]: This is a footnote. You can copy references here and match them to the marks inserts in the plaintext above. -->

<!-- [^2]: NAEP Report Cards - Home. (n.d.). Retrieved March 7, 2018, from https://www.nationsreportcard.gov/# -->

<!-- [^3]: Or maybe they won't?  -->

<!-- [^4]: Religions by Tradition(TR), Religion 2010 (InfoGroup). (n.d.). Social Explorer. Retrieved March 7, 2018, from https://www.socialexplorer.com/tables/Religion_InfoUSA10/R11617373.  -->

<!-- [^5]: Among 15- to 24-year-olds enrolled in grades 10 through 12, percentage who dropped out (event dropout rate), by sex and race/ethnicity: 1972 through 2016. (n.d.). Retrieved March 7, 2018, from https://nces.ed.gov/programs/digest/d17/tables/dt17_219.55.asp?current=yes -->
